\documentclass[pra,superscriptaddress,twocolumn,notitlepage,showpacs]{revtex4-1}
%\documentclass[aps,superscriptaddress,twocolumn,notitlepage,showpacs]{revtex4-1}
%\documentclass[aps,superscriptaddress,twocolumn]{nature}
\usepackage{graphicx} 
\usepackage{amsmath}
 
 
\usepackage{lipsum} % dummy text for the MWE
% Put % before of what you want disabled1
% Select what to do with todonotes: 
%\usepackage[disable]{todonotes} % notes not showed
\usepackage[draft]{todonotes}   % notes showed
% Select what to do with command \comment:  

 
\newcommand{\beq}{\begin{equation}}
\newcommand{\enq}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\ena}{\end{eqnarray}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}


\begin{document}
\title{Quantum emitter dipole-dipole interactions in nanoplasmonic arrays}
\author{M. Ne\v{c}ada, J.-P. Martikainen, and P. T\"{o}rm\"{a}}
\affiliation{COMP Centre of Excellence, Department of Applied Physics,
Aalto University, P.O. Box 15100, Fi-00076 Aalto, Finland}
\date{\today}
%\pacs{33.80.-b, 73.20.Mf, 42.50.Nn}
\pacs{\dots}
%Photon molecule interactions, 33.80.-b
%Plasmons on surfaces and interfaces, 73.20.Mf
%Superfluorescence, 42.50.Nn
%Bose-Einstein statistics, 05.30.-d
%Bose-Einstein condensates, 67.85.Hj, 67.85.Jk
\begin{abstract}
    \dots
\end{abstract}
\maketitle 


\section*{Introduction}
\begin{itemize}
\item Our focus: the effects of dipole-dipole interactions between the emitters
in the nanoplasmonic array system. What could we see in our systems,
i.e. nanoparticle arrays?
\item Mention Salomon's (slit array; FDTD/Bloch equations) and Delga's (single
sphere; Wubs's frequency domain quantum multiple scattering model)
results. Salomon's parameters are probably bit unrealistic in our
context.
\end{itemize}

\section*{Single field mode model}

\emph{This has been done.}


\subsection*{Model description}
\begin{multline}
H=\omega b^{\dagger}b+\sum_{i=1}^{K}\epsilon_{i}S_{i}^{z}+\sum_{i=1}^{K}V_{i}\left(b^{\dagger}S_{i}^{-}+S_{i}^{+}b\right)\\+\sum_{i<j=1}^{K}g_{ij}\left(S_{i}^{+}S_{j}^{-}+S_{j}^{+}S_{i}^{-}\right).
\end{multline}

\begin{itemize}
\item Description: only one field mode, no losses, several dipoles, ...

\begin{itemize}
\item How we calculate couplings for real configurations.
\end{itemize}
\item Excitation number conserved in RWA.
\end{itemize}

\subsection*{Exact diagonalisation results}
\begin{itemize}
\item Spectra for $N\lesssim16$, single excitation subspace
\item Coupling strength effects
\end{itemize}

\subsubsection*{Randomness effects}

Effects of disorder on ``band'' width and position.
\begin{itemize}
\item Directional randomness.
\item Positional randomness.
\end{itemize}

\subsubsection*{Scaling effects}
\begin{itemize}
\item Nearest neighbour approximation shows no qualitative effects at this
tiny scale. This does not necessarily mean that they are negligible
in large systems.
\item Realistic concentrations and dipole moments.

\begin{itemize}
\item What are the quantities for our systems.
\item How do the effects compare to e.g. thermal energy.
\end{itemize}
\end{itemize}

\subsubsection*{Interpretation}
\begin{itemize}
\item Model does not show anything about experimental observables in the
real systems.
\item On the other hand, we can exactly see in the energy spectrum what
can be attributed to the direct d-d interaction and what is mediated.
\item Probably no important effects for realistic concentrations.
\end{itemize}

\section*{Multiple scattering model}

\emph{In progress / not done. Cf. timetable.}


\subsection*{Model description}
\begin{itemize}
\item Brief model description with references to Wubs and Delga
\item The advantage of this model is that it should give an actual observable
light spectrum.
\end{itemize}

\subsection*{Single nanoparticle case}
\begin{itemize}
\item Custom nanoparticle geometry: description, BEM modelling, classical
scattering properties.\emph{ Timetable item 3. }
\item Results: observable spectra for some realistic parameters (QE concentration,
dipole moment). Far field / near field. \emph{Timetable item 6.}
\end{itemize}

\subsection*{Arrays}
\begin{itemize}
\item Similar as in the previous subsection, but now with multiple nanoparticles
in array. \emph{Timetable item 5.}
\item Results: spectra for array geometries. \emph{Timetable item 6.}
\end{itemize}

\section*{Conclusions}

\emph{Not done.}
\begin{itemize}
\item What do the results from the two models tell us about how the dipole-dipole
interactions affect the system. At which parameter regions do we get
some interesting effects.
\item Compare the shape of spectra from the scattering models to the ``simple''
exactly diagonalised model.\end{itemize}
\bibliographystyle{apsrev}
%\bibliography{./bibli_Plasmons_new}


\begin{thebibliography}{31}
\end{thebibliography}


\end{document}
